### 2020-11-24 publications.tex
Update publication

\subsection{Refereed Publications -- \href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{ADS
Search}}}

*Authored by students under direct supervision

\begin{benumerate}{11}
\item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
    factor}\\ Gong, M., Ostriker, E. C., Kim, C.-G., \& \textbf{Kim,
    J.-G.}, \textit{ApJ accepted}
\item \textit{Factories of CO-dark gas: molecular clouds with limited star
formation efficiencies by far-ultraviolet feedback} \\
  Inoguchi, M., Hosokawa, T., Mineshige, S., \& \textbf{Kim, J.-G.} 2020, MNRAS,
  497, 5061I
\item \textit{Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
    Galactic Disks}\\
  $^{*}$Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
  897, 143
\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, ApJ, 883, 102
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Dispersal of Star-Forming Molecular Clouds by UV Radiation
    Feedback: Dependence on Gravitational Boundedness and Magnetic Fields} \\
  \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. \textit{2020, to be
    submitted}
\item[] \textit{Implementation of a Cooling Module for the ISM Coupled with Radiative
    Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim, C.-G., \& Ostriker, E. C.
  \textit{2020, to be submitted}
\item[] \textit{A Theory of Stellar Wind Bubble Expansion in the Turbulent
    ISM}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
  \textit{2020, in preparation}
\item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
    of M15} \\
  Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{2021,
    in preparation}

>>>>

\subsection{Journal Publications -- \href{https://ui.adsabs.harvard.edu/search/filter_database_fq_database=OR&filter_database_fq_database=database\%3A\%22astronomy\%22&fq=\%7B!type\%3Daqp\%20v\%3D\%24fq_database\%7D&fq_database=(database\%3A\%22astronomy\%22)&q=\%3Dauthor\%3A(\%22Kim\%2C\%20Jeong-Gyu\%22)&sort=date\%20desc\%2C\%20bibcode\%20desc}{\color{dodgerblue}{ADS
Search}}}

*Led by a student under direct supervision

\begin{benumerate}{12}
\item \textit{Star Formation Efficiency and Dispersal of Giant Molecular
    Clouds with UV Radiation Feedback: Dependence on Gravitational Boundedness
    and Magnetic Fields} \\ \textbf{Kim, J.-G.}, Ostriker, E. C., \& Filippova, N. arxiv:2011.07772 \textit{(submitted to
    ApJ 10/2020)}
\item \textit{The environmental dependence of the $X_{\mathrm CO}$ conversion
    factor}\\ Gong, M., Ostriker, E. C., Kim, C.-G., \& \textbf{Kim,
    J.-G.} 2020, ApJ, 903, 142 
\item \textit{Factories of CO-dark gas: molecular clouds with limited star
formation efficiencies by far-ultraviolet feedback} \\
  Inoguchi, M., Hosokawa, T., Mineshige, S., \& \textbf{Kim, J.-G.} 2020, MNRAS,
  497, 5061I
\item \textit{$^{*}$Diffuse Ionized Gas in Simulations of Multiphase, Star-forming
    Galactic Disks}\\
  Kado-Fong, E., \textbf{Kim, J.-G.}, Ostriker, E. C., \& Kim, C.-G. 2020, ApJ,
  897, 143
\item \textit{Modeling UV Radiative Feedback from Massive Stars: III. Escape
    of Radiation from Star-Forming Giant Molecular Clouds} \\ \textbf{Kim,
    J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2019, ApJ, 883, 102
\item \textit{Modeling UV Radiative Feedback from Massive Stars: II. Dispersal
of Star-Forming Giant Molecular Clouds by Photoionization and Radiation
Pressure} \\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2018, ApJ, 859,
68
\item \textit{Modeling UV Radiative Feedback from Massive Stars: I.
Implementation of Adaptive Ray Tracing Method and Tests}\\ \textbf{Kim, J.-G.},
Kim, W.-T., Ostriker, E. C.,\& Skinner A. M. 2017, ApJ, 851, 93
\item \textit{Disruption of Molecular Clouds by Expansion of Dusty H II
Regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T., \& Ostriker, E. C. 2016, ApJ, 819,
137
\item \textit{Instability of Magnetized Ionization Fronts Surrounding H II
regions}\\ \textbf{Kim, J.-G.}, Kim, W.-T. 2014, ApJ, 797, 135
\item \textit{Nature of Wiggle Instability of Galactic Spiral Shocks}\\ Kim,
W.-T., Kim, Y., \& \textbf{Kim, J.-G.} 2014, ApJ, 789, 68
\item \textit{Instability of Evaporation Fronts in the Interstellar Medium}\\
  \textbf{Kim, J.-G.}, Kim, W.-T. 2013, ApJ, 779, 48
\item \textit{Gravitational Instability of Rotating, Pressure-Confined,
    Polytropic Gas Disks with Vertical Stratification} \\ \textbf{Kim, J.-G.},
  Kim, W.-T., Seo Y. M., \& Hong, S. S. 2012, ApJ, 761, 131
\end{benumerate}

\subsection{Papers in Preparation}
\begin{enumerate}
\item[] \textit{Implementation of a Module for Heating and Cooling in the ISM
    Coupled with Radiative Transfer}\\ \textbf{Kim, J.-G.}, Gong, M., Kim,
  C.-G., \& Ostriker, E. C. \textit{2020, in preparation}
\item[] \textit{Molecular Cloud Destruction Controlled by Radiation, Winds, and
Supernovae Feedback} \\ \textbf{Kim, J.-G.}, Lancaster, L., Kim, C.-G., \&
Ostriker, E. C. \textit{2021, in preparation}
\item[] \textit{Stellar Wind Bubbles in Turbulent Clouds:
A Fractal Theory Validated with Hydrodynamic Simulations}\\
  Lancaster, L., Ostriker, E. C., \textbf{Kim, J.-G.}, \& Kim, C.-G.,
  \textit{2020, to be submitted 12/2020}
\item[] \textit{r-process Enrichment During the Formation of a Globular Cluster: Case
    of M15} \\
  Hotokezaka, K., \textbf{Kim, J.-G.}, Beniamini, P., \& Cen, R. \textit{2021,
    in preparation}
